NLTK: The Natural Language Toolkit

### 2002-03-18 technical/acl2002/submission.tex
Added summary of NLTK modules from LSA handout
svn/trunk@496

All materials discussed here are available under an open
source license from \url{nltk.sf.net}.

@@

@@

Upbeat conclusion.

Invitation to participate.

>>>>

All materials discussed here are available under an open
source license from \url{nltk.sf.net}.
NLTK runs on most platforms, including Windows, OS X, Linux, and
UNIX.

@@

\section{Modules}

NLTK currently includes the following modules.

\subsection*{Basics}

\begin{description}
\item[token:] Basic classes for processing individual
      elements of text, such as words or sentences. 
\item[tree:] Classes for representing tree structures
      over text (such as syntax trees and morphological trees).
\item[probability:] Classes that encode frequency
      distributions and probability distributions.
\end{description}

\subsection*{Tagging}

\begin{description}
\item[tagger:] A standard interface to tag each token of
      a text with supplementary information, such as its part of
      speech; and several implementations of that interface.
\end{description}

\subsection*{Parsing}

\begin{description}
\item[parser:] A standard interface to produce trees
      representing the structure of texts.
\item[chartparser:] A flexible parser implementation
      that uses a \emph{chart} to record hypotheses about
      syntactic constituents.
\item[srparser\_template:] A partial implementation of a
      shift-reduce parser; completing the implementation was a
      student exercise.
\item[chunkparser:] A standard interface for robust
      parsers used to identify non-overlapping linguistic groups
      (such as noun phrases) in unrestricted text.
\item[rechunkparser:] A regular-expression based
      implementation of the chunk parser interface.
\end{description}

\subsection*{Text Classification}

\begin{description}
\item[classifier:] A standard interface for classifying
      texts into categories.
\item[classifier.feature:] A standard way of encoding
      the information used to make classification decisions.
\item[classifier.naivebayes:] A text classifier
      implementation based on the Naive Bayes assumption.
\item[classifier.maxent:] An implementation of the
      maximum entropy model for text classification; and
      implementations of the GIS and IIS algorithms for training
      the classifier.
\item[classifier.featureselection:] A standard interface
      for choosing which features are relevant for making
      classification decisions.
\end{description}

\subsection*{Visualization}

\begin{description}
\item[draw.tree:] A graphical representation for tree
      structures, such as syntax trees and morphological trees. 
\item[draw.tree\_edit:] A graphical interface used to
      build and modify tree structures.
\item[draw.plot\_graph:] A graphical tool to graph
      arbitrary functions.
\item[draw.chart:] An interactive graphical tool used to
      experiment with chart parsers.
\end{description}

@@

NLTK is an open source project, and we welcome any contributions.  We
deliberately structured NLTK to facilitate parallel development.
Readers who are interested in contributing to NLTK, or who have any
suggestions for improvements, are encouraged to contact the authors.
